Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-05 thesis/paper.tex
Review serialport

We concluded that this change was enhancive as it is a brand-new feature of the API. There was no secondary motive behind this change, as the change was purely enhancive.

%%Explain what she said
The interviewee described how this change and the other changes classified as additions were all included in the new API at the request of API users. Prior to the change being introduced, there was no API functionality for controlling the camera and as such, it was a high priority addition to the new API.

%%Explain how this relates to the category
Based on the interviewees' comments, we concluded that we had correctly identified the change as being enhancive. Furthermore, we were also correct in our prediction that there was no secondary category.

@@

%%Describe the change 
By and large the most common usage of the camera is to analyse video data, however some of the API users require audio data. The inclusion of axaudio allows these users to perform audio analysis upon audio streams captured by Axis devices.

%%Relate it to Categories
This change was also determined to be enhancive as it was an inclusion of a brand-new feature to the API. Similarly to the axptz, there were no suitable sub-categories that could be found to apply to this change.

%%What she said
Audio analysis had not previously been possible on Axis devices. However, the interviewer informed us that an API user had managed to create their own audio analysis using the current (1.4) API. Given the demand for audio analysis, it was a logical choice to include it as a new feature in the new version of the API.

%%Category based on her information
Based on the information available, we concluded that we had successfully determined that the change was enhancive. Once more, there was no supporting evidence to suggest any suitable sub-categories for this change.

@@

%%Describe the change 
Prior to the newest version of the API, storage for the devices existed solely on the cameras or the Video Management System (VMS) itself. The release of version 2.0 saw the inclusion of alternative storage solutions. axstorage now allows Axis devices to interface with external storage devices, such as

Enhancive was once again chosen to be the most applicable category of change given that axstorage was a brand-new inclusion in the newest version of the API. Similarly, there were no appropriate sub-categories for this change.

%%Her information
The limited storage options for the Axis devices meant that this feature was strongly requested by API users and as such was included in this new version of the API.

%%Relate it to Categories
The information gathered from the interview supported that were correct in our choice of enhancive for this change. Once more there was no inclusion of an appropriate subcategory.

>>>>

%%Relate it to Categories
We concluded that this change was enhancive as it is a brand-new feature of the API. There was no secondary motive behind this change, as the change was purely enhancive.

%%What she said
The interviewee described how this change and the other changes classified as additions were all included in the new API at the request of API users. Prior to the change being introduced, there was no API functionality for controlling the camera and as such, it was a high priority addition to the new API.

%%Category based on her information
Based on the interviewees' comments, we concluded that we had correctly identified the change as being enhancive. Furthermore, we were also correct in our prediction that there was no secondary category.

@@

%%Describe the change 
The most important functionality of the camera is to capture and analyse video data, however, some the API users require the possibility to perform analysis upon audio data. The addition of axaudio allows API users to perform audio analysis upon audio streams captured by cameras.

%%Relate it to Categories
This change was determined to be enhancive, as it was an addition of a new feature to the API. We found no secondary motive of the change.

%%What she said
Audio analysis had not previously been possible on Axis devices. During the interview, it was revealed that an API user had managed to implement their own audio analysis using version 1.4 of the API. Given the demand for audio analysis, it was included in version 2.0 of the API.

%%Category based on her information
Based on the the interviewee's reasoning, we concluded that we had successfully determined that the change was enhancive. The addition of axaudio had no secondary motive.

@@

%%Describe the change 
Prior to the newest version of the API being released, the sole alternative for storage was to use the Video Management System. Version 2.0 included the possibility of alternative storage solutions, by allowing to the camera to interface with external storage devices, such as SD cards.

%Relate it to categories
Enhancive was chosen to be the most applicable category of change, given that axstorage was a new addition in version 2.0. No secondary motive was identifed.

%%What she said
The limited storage options for the cameras was the reason that increased functionality was strongly requested by API users and as such axstorage was included in version 2.0 of the API.

%%Category based on her information
The information gathered from the interview supported that we were correct in our categorisation of this change. No secondary category was established.
